### 2015-05-11 evaluation.tex
fix

\noindent
\textbf{Race-Checking}\xspace\xspace Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs that \whoop identified (\#Racy Pairs); number of racy memory regions that \whoop reported (\#Racy MRs); and number of races that \corral discovered (\#Races Found) using a context-switch bound of 2. We did not discover new races with larger context switch bounds. This might mean that these drivers only have races that manifest with at least one or two context-switches, or that \corral hit its bounds before discovering a deeper race.

@@

\noindent
\textbf{Granularity of Context-Switches}\xspace\xspace Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks. All reported times are in seconds and averages of three runs. \corral was given a time budget of 10 hours (T.O. denotes a tool timeout) and a context-switch bound (csb) of 2, 5 and 9. By default, \corral instruments context-switches (i.e. \texttt{yield}) in all visible operations (denoted by \yieldall in the table). \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{whoop:bugfinding}), and also uses all the optimisations discussed in Section~\ref{whoop:optimizations}.

A higher context switch bound results into deeper interleavings being explored and thus a larger sequentialized program. Intuitively, this means that we see even greater speedups using information from \whoop, when exploring deeper interleavings.

>>>>

\noindent
\textbf{Race-Checking}\xspace\xspace Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs that \whoop identified (\#Racy Pairs); number of racy memory regions that \whoop reported (\#Racy MRs); and number of races that \corral discovered (\#Races Found) using a context-switch bound of 2. We did not discover new races with larger context-switch bounds. This might mean that these drivers only have races that manifest with at least one or two context-switches, or that \corral hit its bounds before discovering a deeper race.

@@

\noindent
\textbf{Granularity of Context-Switches}\xspace\xspace Table~\ref{tab:results} presents runtime results from using \whoop, \corral and \whoop + \corral to analyze our benchmarks. All reported times are in seconds and averages of three runs. \corral was given a time budget of 10 hours (T.O. denotes a tool timeout) and a context-switch bound (csb) of 2, 5 and 9. By default, \corral instruments context-switches (i.e. \texttt{yield} statements) in all visible operations (denoted by \yieldall). \whoop + \corral, instead, uses two different context-switch instrumentation granularities, \yieldcoarse and \yieldmr (see Section~\ref{whoop:bugfinding}), and also uses all the optimisations discussed in Section~\ref{whoop:optimizations}.

A higher context-switch bound results into deeper interleavings being explored and thus a larger sequentialized program. Intuitively, this means that we see even greater speedups using information from \whoop, when exploring deeper interleavings.

### 2015-05-11 whoop.tex
fix

Because \corral performs bounded verification both in terms of the number of allowed context switches and loop/recursion unrollings, it is inherently unsound; in other words, it can miss real bugs. On the other hand, \corral is precise, and assuming a precise model of the program environment it will only report true bugs. \whoop takes advantage of this precision to report only feasible data races.

@@

\ZRComment{Could this be cleaned up a bit? In particular, do we need to talk
about entry point pairs, or could we prove it just for any pair?}\PDComment{Lets also see what Ally thinks about this part.}
We now show that our partial-order reduction is sound: it does not miss any more
bugs than what \corral would miss even without taking advantage of the \whoop
race-related information. Let \corral run an $n$ amount of entry point pairs
with yields in all visible operations. Let this configuration be known as $C$.
Each entry point pair is running in a separate \corral process. \corral will
miss all bugs that are triggered by more than 3 bugs running concurrently and
all bugs that are triggered by investigating a larger than $r$ recursion bound
and larger than $k$ context switch bound. Let \corral then run the same $n$
amount of pairs, but this time with all \texttt{yield} statements in non-racy
shared memory accesses that are removed according to information from \whoop. Let this configuration be
known as $W+C$. Because these shared memory accesses cannot race, performing a
\texttt{yield} will not introduce any new program behaviors. Thus, \corral will
find the same bugs using the configuration $W+C$, as using the configuration
$C$.

>>>>

Because \corral performs bounded verification both in terms of the number of allowed context-switches and loop/recursion unrollings, it is inherently unsound; in other words, it can miss real bugs. On the other hand, \corral is precise, and assuming a precise model of the program environment it will only report true bugs. \whoop takes advantage of this precision to report only feasible data races.

@@

\ZRComment{Could this be cleaned up a bit? In particular, do we need to talk
about entry point pairs, or could we prove it just for any pair?}\PDComment{Lets also see what Ally thinks about this part.}
We now show that our partial-order reduction is sound: it does not miss any more
bugs than what \corral would miss even without taking advantage of the \whoop
race-related information. Let \corral run an $n$ amount of entry point pairs
with yields in all visible operations. Let this configuration be known as $C$.
Each entry point pair is running in a separate \corral process. \corral will
miss all bugs that are triggered by more than 3 bugs running concurrently and
all bugs that are triggered by investigating a larger than $r$ recursion bound
and larger than $k$ context-switch bound. Let \corral then run the same $n$
amount of pairs, but this time with all \texttt{yield} statements in non-racy
shared memory accesses that are removed according to information from \whoop. Let this configuration be
known as $W+C$. Because these shared memory accesses cannot race, performing a
\texttt{yield} will not introduce any new program behaviors. Thus, \corral will
find the same bugs using the configuration $W+C$, as using the configuration
$C$.
